### 2022-05-05 supplement.Rmd
Move manuscript and supplement to root dir

---
title             : "Gender differences in infant mental rotation"
shorttitle        : "Infant mental rotation"

author: 
  - name          : "Alexander Enge"
    affiliation   : "1,2,*"
    corresponding : "yes"
    address       : "Stephanstraße 1a, 04103 Leipzig"
    email         : "enge@cbs.mpg.de"
  - name          : "Shreya Kapoor"
    affiliation   : "1,*"
  - name          : "Anne-Sophie Kieslinger"
    affiliation   : "1,*"
  - name          : "Michael A. Skeide"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences"
  - id            : "2"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
  - id            : "*"
    institution   : "These authors contributed equally"

authornote: |
  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}

  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}

  The data and code for this study are openly available at ???.
  We have no conflict of interest to disclose.
  There were no ethical concerns since we did not collect any new data.

abstract: |
  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months. We robustly found that male infants recognized novel rotated objects more reliably than female infants. The effect size of this average difference was small and did not change with age. These findings indicate that gender differences in mental rotation are already present in the first months of life.

keywords          : "mental rotation, spatial cognition, spatial ability, infants, children, gender, meta-analysis"
wordcount         : "X"

bibliography      : "references.bib"
csl               : "nature.csl"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

```{r, setup, include=FALSE}
# Load packages
library(papaja)
library(here)
library(readxl)
library(scales)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)
library(bayestestR)
library(tidybayes)
library(cowplot)

# Global chunk options
knitr::opts_chunk$set(
  include = FALSE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%",
  warning = FALSE
)

# Directory paths
data_dir <- here("data")
figures_dir <- here("results/figures")
tables_dir <- here("results/tables")

# Download literature search spreadsheet from Google Drive
excel_url <- "https://docs.google.com/spreadsheets/d/1xnC0NlQYTXavXaeqQidhi7UKb1pCGAl9Ry3h3Uz3mi0"
excel_file <- here(data_dir, "literature_search.xlsx")
# googledrive::drive_auth(use_oob = TRUE)
# googledrive::drive_download(excel_url, excel_file, overwrite = TRUE)

# Read sheets
screening <- read_excel(excel_file, sheet = "screening")
included <- read_excel(excel_file, sheet = "included", na = "NA")
gender <- read_excel(excel_file, sheet = "gender_differences", na = "NA")

# Add columns to the table of included experiments
included %>%
  mutate(

    # Add unique experiment identifier
    experiment = str_c(year, article, group_long, sep = ", "),

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired t test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F value via conversion to a t value
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard devations
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
    d_av = mean_diff / sd_av,
    # Add d from one-sample t test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,

    # Choose one type of outcome variable for each experiment
    di = case_when(
      # 1. If d was reported directed
      !is.na(d) ~ d,
      # 2. If a paired sample t test was reported
      !is.na(d_z_t) ~ d_z_t,
      # 3. If ANOVA was reported
      !is.na(d_z_f) ~ d_z_f,
      # 4. If the difference between means and its SD were reported
      !is.na(d_z_diff) ~ d_z_diff,
      # 5. If the individual condition means and their SDs were reported
      !is.na(d_av) ~ d_av,
      # 6. If a novelty preference score and its SD were reported
      !is.na(d_nov_pref) ~ d_nov_pref
    ),
    # Keep track which type of outcome measure was chosen for each article
    di_type = case_when(
      !is.na(d) ~ "d",
      !is.na(d_z_t) ~ "d_z_t",
      !is.na(d_z_f) ~ "d_z_f",
      !is.na(d_z_diff) ~ "d_z_diff",
      !is.na(d_av) ~ "d_av",
      !is.na(d_nov_pref) ~ "d_nov_pref",
      TRUE ~ "none"
    ) %>%
      factor(levels = c(
        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
      )),

    # Apply small sample correction using Hedges' exact method
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    dfi = 2 * (sample_size - 1),
    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
    gi = di * ji,

    # Recode gender as a categorical (factor) variable for meta-regression
    gender = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),

    # Recode mean sample age in years (centered) for meta-regression
    age = age_mean / 365.25,
    age_c = age - mean(age, na.rm = TRUE),
    age_sd = age_sd / 365.25,

    # Recode task type as a categorical (factor) variale for meta-regression
    task = factor(task, levels = c("Habituation", "VoE")),

    # Combine gender and task into one column for plotting
    gender_task = factor(
      str_c(gender, task, sep = ", "),
      levels = c(
        "Female, Habituation",
        "Male, Habituation",
        "Mixed, Habituation",
        "Mixed, VoE"
      )
    )
  ) %>%
  # Order rows by experiment ID
  arrange(experiment) -> dat_all

# Overview of the different effect sizes
dat_all %>%
  select(
    article,
    group,
    gender_split,
    gi,
    di,
    di_type,
    d,
    d_z_t,
    d_z_f,
    d_z_diff,
    d_av,
    d_nov_pref
  ) %>%
  print(n = Inf)

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) -> dat_all_r

# Show number of experiments per gender grouping strategy
table(dat_all_r$gender_split)

# Extract split or mixed experiments only
dat_split <- filter(dat_all_r, gender_split %in% c("split", "split_only"))
dat_mixed <- filter(dat_all_r, gender_split %in% c("mixed", "mixed_only"))

# Combine both strategies, preferring split experiments
dat_both_split <- filter(
  dat_all_r, gender_split %in% c("split", "mixed_only", "split_only")
)

# Combine both strategies, preferring mixed experiments
dat_both_mixed <- filter(
  dat_all_r, gender_split %in% c("mixed", "mixed_only", "split_only")
)

# We go ahead with the last solution as to use the maximum amount of information
# while not biasing the gender results
dat <- dat_both_mixed

# Helper functions to re-format age from days to months + days
format_days_months <- function(days, long = FALSE) {
  m_str <- ifelse(long, " months ", "m ")
  d_str <- ifelse(long, " days", "d")
  days_per_month <- 30.417
  months <- days %/% days_per_month
  days_left <- as.integer(days - months * days_per_month)
  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
  str[is.na(days)] <- NA
  return(str)
}

# Helper function for printing percentages
print_perc <- function(x) scales::percent(x, accuracy = 0.1)

# Extract some descriptive statistics for usage in the main text
descs <- list(
  n_experiments = nrow(dat),
  n_infants = sum(dat$sample_size),
  percent_female = mean(dat$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
  mean_age_weighted = format_days_months(
    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat, task == "VoE"))
)
```

# Introduction

The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020]. Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].

Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013]. Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$). Interestingly, a recent meta-analysis [@lauer2019a] in 3-17-year-old children and adolescents suggests even only a small-to-medium difference (mean weighted $g = 0.39$). Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.

In the present study, we meta-analyzed `r descs$n_experiments` effect sizes derived from looking times in mental rotation tasks conducted by `r formatC(descs$n_infants, big.mark = ",")` infants (`r print_perc(descs$percent_female)` female) aged `r descs$min_age_months` to `r descs$max_age_months` months (mean age of `r descs$mean_age_weighted`; Supplementary Table 1). All tasks were embedded either into habituation experiments (`r descs$n_experiments_habituation`) or violation of expectation experiments (`r descs$n_experiments_voe`) [@fantz1964; @baillargeon1985]. These experiments comprised real world stimuli (e.g., toy objects [@antrilli2016]), three-dimensional digital stimuli (e.g., cube figures [@moore2008]), or two-dimensional digital stimuli (e.g., digits [@quinn2008]). In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object. Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation. In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle. Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle. Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown. Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle. In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.

Following previous work in older populations, we hypothesized that looking times in mental rotation experiments are on average significantly longer in male compared to female infants. Effect sizes were assumed to be small.

# Results

## Mental rotation performance

```{r, meta_analysis}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
n_iter <- 4000
n_warmup <- 1000
n_chains <- 4
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  file = here("results", "models", "res_prior")
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(
  res_prior,
  sample_prior = FALSE,
  file = here("results", "models", "res_brm")
)
summary(res_brm)
# plot(res_brm)

# Get posterior probability mass > 0 for the meta-analytic effect
(hyp_brm <- hypothesis(res_brm, "Intercept > 0")$hypothesis)

# # Summarise fixed effects (incl. Bayes factors)
# describe_posterior(
#   res_brm,
#   centrality = "mean", ci = 0.95, ci_method = "ETI",
#   test = c("p_direction", "rope", "bayesfactor"),
#   rope_range = c(-0.1, 0.1)
# )

# Extract posterior draws for the meta-analytic effects
spread_draws(res_brm, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC
  mutate(
    intercept = b_Intercept,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sigma_article^2,
    sigma2_experiment = sigma_experiment^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
    .keep = "unused"
  ) -> draws_brm

# Summarize as mean and 95% credible intervals
(summ_brm <- as.list(mean_qi(draws_brm)))
```

```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
# Helper functions for printing numbers with exactly 2 decimal points
print_num <- function(x, digits = 2) {
  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
  x[x == "NA"] <- NA
  return(x)
}

# Helper function for confidence intervals (optionally adding the mean)
print_ci <- function(lb, ub, mean = NULL) {
  mean_str <- ifelse(mean, paste0(print_num(mean), " "))
  paste0(mean_str, "[", print_num(lb), ", ", print_num(ub), "]")
}

# Get posterior draws for the effect in each experiment
epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(ci_lb, ci_ub, mean = gi)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm$intercept),
      print_num(summ_brm$intercept.lower),
      print_num(summ_brm$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descs$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descs$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
```

(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants. White squares depict the effect sizes (Hedges’ $g$) for infants’ mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals. Gray bars indicate the 95% and 50% Bayesian credible intervals (CrI). These intervals got shrunk towards the meta-analytic effect size because of partial pooling which regularized the impact of experiments with small sample sizes or unrealistically large effect sizes to prevent overfitting the model. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects. Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig. 1). The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level. Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_brm$icc)` was attributable to differences *between* articles.

## Effects of gender, age, and task type

```{r, meta_regression}
# Set numerical contrasts for factor variables
contrasts(dat$gender) <- MASS::contr.sdif(3)
contrasts(dat$task) <- MASS::contr.sdif(2)

# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
  set_prior("normal(0, 0.5)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  file = here("results", "models", "res_prior_reg")
)
summary(res_prior_reg)
# plot(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here("results", "models", "res_brm_reg")
)
summary(res_brm_reg)
# plot(res_brm_reg)

# Get posterior probability mass > 0 for all regression weights
(hyps_brm_reg <- list(
  intercept = hypothesis(res_brm_reg, "Intercept > 0")$hypothesis,
  female_mixed = hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis,
  male_female = hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis,
  age = hypothesis(res_brm_reg, "age_c > 0")$hypothesis,
  voe_habituation = hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis,
  female_mixed_age = hypothesis(res_brm_reg, "gender2M1:age_c > 0")$hypothesis,
  male_female_age = hypothesis(res_brm_reg, "gender3M2:age_c > 0")$hypothesis
))

# # Summarise fixed effects (incl. Bayes factors)
# describe_posterior(
#   res_brm_reg,
#   centrality = "mean", ci = 0.95, ci_method = "ETI",
#   test = c("p_direction", "rope", "bayesfactor"),
#   rope_range = c(-0.1, 0.1)
# )

# Extract posterior draws for the meta-analytic effects
spread_draws(res_brm_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC
  mutate(
    intercept = b_Intercept,
    female_mixed = b_gender2M1,
    male_female = b_gender3M2,
    age = b_age_c,
    voe_habituation = b_task2M1,
    female_mixed_age = `b_gender2M1:age_c`,
    male_female_age = `b_gender3M2:age_c`,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sd_article__Intercept^2,
    sigma2_experiment = `sd_article:experiment__Intercept`^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
  ) -> draws_brm_reg

# Summarize as mean and 95% credible intervals
(summ_brm_reg <- as.list(mean_qi(draws_brm_reg)))
```

As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Fig. 2).
Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_brm_reg$male_female`$, 95% CrI [`r summ_brm_reg$male_female.lower`, `r summ_brm_reg$male_female.upper`].
The probability for this effect being larger than zero was `r print_perc(hyps_brm_reg$male_female$Post.Prob)`.
We found no difference between mixed-gender and all-female samples, $b = `r -summ_brm_reg$female_mixed`$, 95% CrI [`r -summ_brm_reg$female_mixed.lower`, `r -summ_brm_reg$female_mixed.upper`] (`r print_perc(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero).
Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_brm_reg$age`$, 95% [`r summ_brm_reg$age.lower`, `r summ_brm_reg$age.upper`].
We also did not detect an interaction between gender and age ([females - mixed] × age: $b = `r summ_brm_reg$female_mixed_age`$, 95% CrI [`r summ_brm_reg$female_mixed_age.lower`, `r summ_brm_reg$female_mixed_age.upper`]; [males - females] × age: $b = `r summ_brm_reg$male_female_age`$, 95% CrI [`r summ_brm_reg$male_female_age.lower`, `r summ_brm_reg$male_female_age.upper`]).
Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_brm_reg$voe_habituation`$, 95% [`r summ_brm_reg$voe_habituation.lower`, `r summ_brm_reg$voe_habituation.upper`].
The probability for this effect being greater than zero was `r print_perc(hyps_brm_reg$voe_habituation$Post.Prob)`.

```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
# Get draws from the posterior distribution
draws_reg <- epred_draws(
  res_brm_reg,
  dat,
  ndraws = NULL,
  re_formula = NA
)

# Use colors as proposed in https://arxiv.org/abs/2107.02270
habi_colors <- c(
  "Female, Habituation" = "#5790fc",
  "Male, Habituation" = "#f89c20",
  "Mixed, Habituation" = "#e42536"
)
voe_colors <- c("Mixed, VoE" = "#964a8b")

# Regression plot
dat %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
  annotate(
    "rect",
    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
    color = NA, fill = "white"
  ) +
  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    fill = NA,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "CrI level",
    size = "Sample size"
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_reg

# Extract the legend so that we can put it inside the plotting area
plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))

# Define new labels for the regression coefficients
coef_colnames <- c(
  "Intercept" = "b_Intercept",
  "Females - mixed" = "b_gender2M1",
  "Males - females" = "b_gender3M2",
  "Age (per year)" = "b_age_c",
  "Habituation - VoE" = "b_task2M1",
  "(Females - Mixed) × age" = "b_gender2M1:age_c",
  "(Males - Females) × age" = "b_gender3M2:age_c"
)

# Plot posterior distributions of the regression coefficients
draws_reg_coef <- tidy_draws(res_brm_reg)
draws_reg_coef %>%
  select(all_of(coef_colnames)) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
  annotate(
    "text",
    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
    family = "Helvetica", fontface = "bold", color = "black"
  ) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(colour = "black"),
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_text(
      family = "Helvetica", color = "black", size = 3.88 * .pt,
      hjust = 0, vjust = -0.1, margin = margin(l = 20)
    ),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_coef

# Combine plots
plot_grid(
  plot_reg, plot_coef,
  nrow = 1, rel_widths = c(3, 2), labels = "auto",
  label_size = 11, label_fontfamily = "Helvetica",
  label_x = 0.008, label_y = 0.99
) +
  draw_plot(plot_reg_legend, x = 0.385, y = 0.865, hjust = 0.5, vjust = 0.5)

# Save plot
ggsave(here(figures_dir, "regression_coef.pdf"), width = 12, height = 5)
```

(ref:fig2-caption) **Effects of gender, age, and task.** **a,** Squares show the effect size (Hedges’ g) for infants’ mental rotation performance in each of the 59 individual experiments. Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample). Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 95% and 50% credible interval (CrI). **b,** Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 95% Crl (thin black lines) and 50% Crl (thick black lines). Gray curves indicate the posterior distribution for each effect.

```{r, gender_differences}
# Extract relevant effect sizes
gender %>%
  # Remove redundant samples
  filter(!redundant) %>%
  # Add columns
  mutate(

    # Add unique experiment identifier
    experiment = str_c(year, article, group_long, sep = ", "),

    # Re-code non-significant f values as an effect of 0
    f = as.numeric(f),
    f_assumed = ifelse(is.nan(f), 0, f),

    # Add d from two-samples t test (Lakens, 2013)
    d_t = t * sqrt(1 / female_n + 1 / male_n),

    # Add d from ANOVA F value via conversion to a t value
    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),

    # Add d from mean difference and pooled standard deviation
    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
      (female_n - 1) * (mean_diff_females_sd^2),
    df = male_n + female_n - 2,
    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
    d_diff = mean_diff / sd_diff_pooled,

    # Add d from one-sample t test of novelty preference scores
    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
      (female_n) * (novelty_pref_females_sd^2),
    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,

    # Choose one type of outcome variable for each experiment
    di = case_when(
      # 1. If d was reported directed
      !is.na(d) ~ d,
      # 2. If a t test was reported
      !is.na(d_t) ~ d_t,
      # 3. If ANOVA was reported
      !is.na(d_f) ~ d_f,
      # 4. If the difference between means and their SDs were reported
      !is.na(d_diff) ~ d_diff,
      # 5. If novelty preference scores and their SDs were reported
      !is.na(d_nov_pref) ~ d_nov_pref
    ),
    # Keep track which type of outcome measure was chosen for each article
    di_type = case_when(
      !is.na(d) ~ "d",
      !is.na(d_t) ~ "d_t",
      !is.na(d_f) ~ "d_f",
      !is.na(d_diff) ~ "d_diff",
      !is.na(d_nov_pref) ~ "d_nov_pref"
    ) %>%
      factor(levels = c("d", "d_t", "d_f", "d_diff", "d_nov_pref")),

>>>>

<!-- Re-define labels for tables and figures -->
\captionsetup[table]{name=Supplementary Table}
\captionsetup[figure]{name=Supplementary Fig.}

<!-- Restart numbering of figures, tables, equations, and pages -->
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\theequation}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{equation}{0}
\setcounter{page}{1}
